### 2018-02-28 Paper/jaccardbaetica.tex
update conclusion

Our case study examines the relation between the distribution of amphoric stamps and the workshops. We analysed a dataset of 990 stamps from 81 workshops. A sample of 131 different stamps were identified and collected from CEIPAC database (citar). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance.

@@

\subsection{Dissimilarity correlation}

@@

@@

No similarity between stamps and amphora workshops were founded.

@@

>>>>

Our case study examines the relation between the distribution of amphoric stamps and the workshops. We studied a dataset of 3787 stamps collected from CEIPAC database (CITAR). However, the 70 \% of stamps cannot be tested due to fragmentation or imcomplete information. Consequently, we discard integrate the fragmented stamps in our dataset.

We finally filter a total sample of 990 stamps composed by 131 different stamps from 81 workshops. The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance.

@@

\subsection{Quantifying the diversity Dissimilarity correlation}

@@

The analysis shows that amphoric stamps are not correlated with spatial distance. A matrix distance of similarity between workshops can be seen in Fig.1. The matrix displays

Morisita-Horn dissimilarities

A dendrogram was generated

@@

No strong similarity between stamps and amphora workshops were found.

@@

It could be due to several reason. On the one hand, the use of this amphoric stamps were exclusively running by the owner or family to distinguish the amphora workshop (CITAR). On the other, it could be somehow a batch sistematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases.

just 30-40 \% of amphora Dressel 20 was marked 
An any case, 
Considering,
